
We clean the memory and charge the libraries

```{r}
rm(list=ls())

library(fpp2)
library(tseries)
```

We assign a variable with the time series of the train data


```{r}
tr_PM10_24h_00 <- read.csv("~/It Academy/Data Science/Aire/tr_PM10_24h_00.csv", row.names=1)
```


We execute auto.arima to find the optimal parameters of the model


```{r}
mod.tr_PM10_24h_00 <- auto.arima(tr_PM10_24h_00, trace=TRUE, allowdrift=FALSE)
```

The best model is ARIMA (1,0,0). We create a model with this parameters and the train data

```{r}
mod.tr_PM10_24h_00 <- Arima(tr_PM10_24h_00[,1], order=c(1,0,0))
```

We evaluate the accuracy of the prediction model, in this case the one step forecasting is executed on the train data 

```{r}
accuracy(mod.tr_PM10_24h_00)
```

We assign a variable with the time series of the test data


```{r}
te_PM10_24h_00 <- read.csv("~/It Academy/Data Science/Aire/te_PM10_24h_00.csv", row.names=1)
```

We perform a one step forecast in the data test using the model with the fitted parameters from the train data

```{r}
mod.te_PM10_24h_00<- Arima(te_PM10_24h_00[,1], model=mod.tr_PM10_24h_00)
```

We evaluate the accuracy of the model on the test data,

```{r}
accuracy(mod.te_PM10_24h_00)
```

We write a csv with the values of the time series forecast of the data test

```{r}
write.csv(mod.te_PM10_24h_00[["fitted"]],"C:\\Users\\hinoj\\OneDrive\\Documentos\\It Academy\\Data Science\\Aire\\fr_PM10_24h_00.csv")
```

